---
title: "Alcohol vs Seat choice"
author: "Veronica Flores"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
```{r eval=FALSE}
FinalData <- davisdata %>%
mutate(across(where(is.character), as.factor))
```
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
      This graph tells us that the people who sit in the back drik more alchohol thank the people who sit in the front.The median at the front is at 0 while the median around the middle is at 1 or 2. And the median in the back is at 4 or 5. so as you move to the back the more students that consume more alchohol increases. 
  


## Numerical Summarys 

## Inferential Tests

## Conclusions


