---
title: "Alcohol vs Seat choice"
author: "Veronica Flores"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
```{r eval=FALSE}
FinalData <- davisdata %>%
mutate(across(where(is.character), as.factor))
```
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
      This graph tells us that the people who sit in the back drik more alchohol thank the people who sit in the front.The median at the front is at 0 while the median around the middle is at 1 or 2. And the median in the back is at 4 or 5. so as you move to the back the more students that consume more alchohol increases. 
  


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

The data shows us that the mean set of the front is 1.8, the ,iddle is 3.28 and the back is 9.6. Which means this is showing us the back has a larger mean than the front and the middle which means the back has a larger alchohol consumption.  
## Inferential Tests

## Conclusions


